Synthesizing Verified Components~~~\\ for Cyber Assured Systems Engineering~ \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2021-08-01 paper/paper.tex
Added badges around paper title

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{comment}
\usepackage{paralist}
\usepackage{graphicx}
\graphicspath{{./figs/}} 
\usepackage{listings}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{flushend}

@@

\begin{document}
\title{
  Synthesizing Verified Components for Cyber Assured Systems Engineering 
  \thanks{DISTRIBUTION STATEMENT A.  Approved for public release.}
}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{comment}
\usepackage{paralist}
\usepackage{graphicx}
\graphicspath{{./figs/}} 
\usepackage{listings}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{flushend}
\usepackage{hyperref}
\usepackage[firstpage]{draftwatermark}

\SetWatermarkAngle{0}
\SetWatermarkFontSize{8pt}
\SetWatermarkText{\raisebox{\textheight}{%
\begin{minipage}{\textwidth}%
\vspace{-18pt}\hfill%
\href{http://doi.org/10.5281/zenodo.5129276}{% REPLACE WITH YOUR ARTIFACT DOI
\includegraphics[width=0.6in, height=0.6in]{reusable}% IF REUSABLE BADGE GRANTED
\includegraphics[width=0.6in, height=0.6in]{available}% IF AVAILABLE BADGE GRANTED
}
\end{minipage}%
}}

@@

\begin{document}
\title{
  Synthesizing Verified Components~~~\\
  for Cyber Assured Systems Engineering~
  \thanks{DISTRIBUTION STATEMENT A.  Approved for public release.}
}
